Modern BTree techniques

### 2022-09-16 strangeloop/presentation.tex
Add learned index

>>>>

    \begin{center}
    \textbf{Learned Index}
    \vspace{1.0cm}

    \begin{overprint}[3cm]
        \onslide<1>
        \begin{tikzpicture}[]
            \smallbtree{1}{2.5}{}{}{}{green-box}
            \node[dp-tree-log, below=1.5cm of nodebox1.south] (log2) {};
            \node[dp-tree-log, right=0.5cm of log2] (log3) {};
            \node[dp-tree-log, left=0.5cm of log2] (log1) {};
            \draw[->, btree-line] (nodebox1.south) -- (log3);
            \draw[->, btree-line] (nodebox1.south) -- (log2);
            \draw[->, btree-line] (nodebox1.south) -- (log1);
            \draw[->, btree-line] (log1) -- (log2) -- (log3);
        \end{tikzpicture}

        \onslide<2>
        \begin{tikzpicture}[]
            \node[green-box,
                  rounded corners=0.2cm,
                  inner sep=0.2cm,
                  minimum width=3.23cm,
                  minimum height=2.23cm,
                  right=1cm of nodebox1]
                (unknown-box) {?};
            \node[dp-tree-log, below=1.5cm of unknown-box.south] (log2) {};
            \node[dp-tree-log, right=0.5cm of log2] (log3) {};
            \node[dp-tree-log, left=0.5cm of log2] (log1) {};
            \draw[->, btree-line] (unknown-box.south) -- (log3);
            \draw[->, btree-line] (unknown-box.south) -- (log2);
            \draw[->, btree-line] (unknown-box.south) -- (log1);
            \draw[->, btree-line] (log1) -- (log2) -- (log3);
        \end{tikzpicture}

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        Kraska Tim, Alex Beutel, Ed H. Chi, Jeffrey Dean, and Neoklis
        Polyzotis. "The case for learned index structures." In Proceedings of
        the 2018 international conference on management of data.
    \linespread{1.5}

    \end{center}
\end{frame}
\note{
}
